Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-04-04 PAPER.tex
re-compiled all PS plots with sigloss v8

Going forward, we treat every $k$-value separately in order to determine an upper limit on the EoR signal per $k$. We bin our simulation outputs along the $P_{\rm in}$ axis, and smooth the distribution of $\widehat{P}_{\rm out}$ values using kernel density estimators (\citealt{scott2008kernel}) for each bin (and normalizing them). Stitching all of them together results in a 2-dimensional smoothed transfer function, shown in Figure \ref{fig:sigloss_transfercurve} for both the weighted (left) and unweighted (right) cases. Although we only show figures for one $k$-value, we note that 
the shape of the transfer curve is similar for all $k$'s. This transfer function is the likelihood function in Bayes' rule, namely $\mathcal{L} (  \widehat{P}_{\rm out} | P_{\rm in})$.  We then invoke Bayes' interpretation and re-interpret it as the posterior $p(P_{\rm in}|\widehat{P}_{\rm out})$ where we recall that $\widehat{P}_{\rm out}$ is a model of our data. To do this we make a horizontal cut across at the data value $\widehat{\textbf{P}}_{x}$ (setting $\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{x}$) and multiply by our prior to yield a posterior distribution for the signal. We compute the $95\%$ confidence interval (an upper limit on EoR) from these distributions.

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop_2panel.pdf}
	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$\,$h$ Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Top: Values 
are shown before (gray) and after (black) signal loss estimation as a function of number of eigenmodes of $\widehat{\textbf{C}}$ that 
are down-weighted. This regularization knob is tuned from $0$ modes on the left (i.e. unweighted) to $21$ modes on the right (i.e. the full inverse 
covariance estimator). Over $\sim3$ orders of magnitude of signal loss results when using empirically estimated inverse covariance weighting. Bottom: Power spectrum upper limits before (gray) and after (black) signal loss estimation as a function of identity added to the empirical covariance. This regularization knob is tuned from $\gamma = 10^{-4}$ on the right (i.e. very little regularization) to $\gamma = 1$ on the left (see main text for the definition of $\gamma$). Also 
plotted in both panels for comparison are $2\sigma$ power spectrum upper limits for the uniform-weighted case (dashed blue) and inverse variance 
weighted case (red); both are after signal loss estimation. Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
as solid green. In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}}_{\rm eff} \equiv 0.035 \, $Tr($\widehat{\textbf{C}})\textbf{I} + \widehat{\textbf{C}}$ ($\gamma = 0.035$) as a simple example of regularization that minimizes loss, and note that the power spectrum limits are roughly constant across a large range of values of $\gamma$.}
	\label{fig:sigloss_modeloop}
\end{figure*}

>>>>

Going forward, we treat every $k$-value separately in order to determine an upper limit on the EoR signal per $k$. We bin our simulation outputs along the $P_{\rm in}$ axis, and smooth the distribution of $\widehat{P}_{\rm out}$ values using kernel density estimators (\citealt{scott2008kernel}) for each bin (and normalizing them). Stitching all of them together results in a 2-dimensional smoothed transfer function, shown in Figure \ref{fig:sigloss_transfercurve} for both the weighted (left) and unweighted (right) cases. Although we only show figures for one $k$-value, we note that 
the shape of the transfer curve is similar for all $k$'s. This transfer function is the likelihood function in Bayes' rule, namely $\mathcal{L} (  \widehat{P}_{\rm out} | P_{\rm in})$.  We then invoke Bayes' interpretation and re-interpret it as the posterior $p(P_{\rm in}|\widehat{P}_{\rm out})$ where we recall that $\widehat{P}_{\rm out}$ is a model of our data. To do this we make a horizontal cut across at the data value $\widehat{\textbf{P}}_{x}$ (setting $\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{x}$) and assume a uniform prior to yield a posterior distribution for the signal. We compute the $95\%$ confidence interval (an upper limit on EoR) from these distributions.

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop_2panel.pdf}
	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$\,$h$ Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Top: Values 
are shown before (gray) and after (black) signal loss estimation as a function of number of eigenmodes of $\widehat{\textbf{C}}$ that 
are down-weighted. This regularization knob is tuned from $0$ modes on the left (i.e. unweighted) to $21$ modes on the right (i.e. the full inverse 
covariance estimator). Over $\sim3$ orders of magnitude of signal loss results when using empirically estimated inverse covariance weighting. Bottom: Power spectrum upper limits before (gray) and after (black) signal loss estimation as a function of identity added to the empirical covariance. This regularization knob is tuned from $\gamma = 10^{-4}$ on the right (i.e. very little regularization) to $\gamma = 1$ on the left (see main text for the definition of $\gamma$). Also 
plotted in both panels for comparison are $2\sigma$ power spectrum upper limits for the uniform-weighted case (dashed blue) and inverse variance 
weighted case (red); both are after signal loss estimation. Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
as solid green. In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}}_{\rm eff} \equiv 0.035 \, $Tr($\widehat{\textbf{C}})\textbf{I} + \widehat{\textbf{C}}$ ($\gamma = 0.035$) as a simple example of regularization that minimizes loss, and note that the power spectrum limits using this type of regularization are roughly constant across a large range of values of $\gamma$.}
	\label{fig:sigloss_modeloop}
\end{figure*}
